\documentclass{letter}

\signature{Evan Gravelle}
\address{4885 Cole St. Unit 31 \\ San Diego, CA, 92117}
\longindentation=0pt
\telephone{(805) 205-4318}
% \date{November 2, 2016}
\begin{document}
\begin{letter}{Google people \\ Mountain View}
\opening{Dear dude,}
why you think you'd be great for the Google Brain Residency Program
The goal of the residency program is to help residents become productive and successful deep learning researchers.
jump-start your career in deep learning
Things to talk about: being well-versed in state of the art AI literature.
 applicants should be passionate about the science of machine learning. 
Candidates should possess a strong interest in the field, a commitment to detail, and a passion for deep learning
Evidence of proficiency in programming and in the prerequisite courses in the form of a transcript, letters of recommendation, notable performance in competitions, or links to an open-source project that demonstrates programming and mathematical ability.
Responsibilites:
Understand a large body of research in deep learning quickly.
Work with your research mentors to formulate research project(s) and/or novel application(s) of the technology.
Conduct research and publish it in competitive venues.
Implement algorithms in TensorFlow.

ME -> controls (enjoy programming) -> robotics -> traffic networks (Q-learning is best current method)-> CSE250A -> Summer of AI (Barto/Sutton, David Silver, Andrew Ng, NN textbook, Atari paper, AlphaGo paper, python, tensorflow)-> CSE250B -> pong
\closing{Sincerely,}
\end{letter}
\end{document}
